---
title: "Classifying bad passwords into categories"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction 

For this project I wanted to implement a machine learning model on a [TidyTuesday](https://www.tidytuesday.com/) dataset. I don't have a lot of practical experience with classification tasks so I chose a data set that lended itself well to those algorithms. This machine learning task is a **supervised learning**  as the data already has labels assigned to it. 
I intially explored using several classification algorithms to train a model and classify the passwords; however as machine learning algorithms generally don't handle text data well I had to do some data preprocessing and transformation. 

# Data 

```{r}
# load in packages for tidy evaluation
library(ggplot2)
library(dplyr)
library(caret)
library(FeatureHashing)
library(xgboost)

# read password data set into R
passwords <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-14/passwords.csv')

# get an idea of the data
summary(passwords)

# peek at the beginning of the data
head(passwords)
tail(passwords)
any(is.na(passwords))
colSums(is.na(passwords))
#removes the na's from the tibble 
passwords_tidied <- passwords[1:500, 1:9]
# confirms we have removed all the nas  
any(is.na(passwords_tidied))

```

